### 2017-12-28 Paper/bg.tex
working on the borehole example
work in progess

For parameters with continuous distributions, the upper bound on the total Sobol' sensitivity index
can be expressed in terms of $\mu_i$, the Poincar\'e constant ($\mathcal{C}_i$) and the total 
variance of the model output ($V$)~\cite{Lamboni:2013}:

\be
ST_i \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i})
\label{eq:bound}
\ee

@@

\be
\hat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
\ee

@@

\be
\bm{c} = \mathbb{E}[\Psi_\alpha(\bm{\xi})\cdot\mathcal{Y}]
\approx
\sum_{i=1}^{N} \mathcal{Y}(\bm{\theta}^{(i)})w^{(i)}\Psi_\alpha(\bm{\xi}^{(i)})
\ee

@@

\be
\hat{\bm{c}} = \mbox{argmin}~\mathbb{E}\left[\left(\bm{c}^{T}\Psi(\bm{x}) -
\mathcal{M}(\bm{x})\right)^{2}\right]  + \lambda\normone{\bm{c}}
\ee

>>>>

For parameters with continuous distributions, the upper bound on the total 
Sobol' sensitivity index ($\mathcal{T}(\theta_i)$)
can be expressed in terms of $\mu_i$, the Poincar\'e constant ($\mathcal{C}_i$) and the total 
variance of the model output ($V$)~\cite{Lamboni:2013}:

\be
\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i})
\label{eq:bound}
\ee

@@

\be
\hat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
\label{eq:cmu}
\ee

@@

\be
\bm{c} = \mathbb{E}[\Psi_\alpha(\bm{\xi})\cdot\mathcal{Y}^{\mbox{\tiny{M}}}]
\approx
\sum_{i=1}^{N} \mathcal{Y}^{\mbox{\tiny{M}}}(\bm{\theta}^{(i)})w^{(i)}\Psi_\alpha(\bm{\xi}^{(i)})
\ee

@@

\be
\hat{\bm{c}} = \mbox{argmin}~\mathbb{E}\left[\left(\bm{c}^{T}\Psi(\bm{\bm{\xi(\theta)}}) -
\mathcal{Y}^{\mbox{\tiny{M}}}(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}}
\ee
